---
title: "Price Range for Diamonds"
author: "Soo Ingrisone"
date: "8/13/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Documentation for a user 

The purpose of the documentation is for a user to get started using the shiny application for the price range of diamonds.

The main function of the application is to provide a user the price range information of the diamonds based on user's 4C selections (carat, cut, color and clarity). The application is interactive: 

- **Carat**: the range of carat values can be chosen using slider.

- **Cut, color, clarity**: one option can be selected for each category by selecting one radio button. 


## Documentation for a user (Cont.)

Once a user makes any of 4C selections, the application will automatically update its associated results on the main panel. 

A user will be provided with the following information in the main panel:

- **min/max** of price range 

- **mean** price based on user's selections

- **histogram** of the price based on the user's choices


## File locations

- Shiny site for the price range of diamonds is here:

https://singrisone.shinyapps.io/PriceDiamonds/


- R program files, documentation and R studio presenter file are stored here:

https://github.com/singrisone/Shiny_Price_of_Diamonds

https://rpubs.com/singrisone/648851

## Data Used

The data used for this application is *diamonds*, which is available via **ggplot2** package and contains the prices and other attributes of diamonds. The application utlizes the *price, carat, cut, color and clarity* of the data.

```{r, echo=TRUE, comment= ''}
library("ggplot2")
dia <- as.data.frame(diamonds[,c(1:4,7)])
head(dia)
```



